Software Citation Principles

### 2016-02-19 sc-principles/software-citation-principles.tex
Adding some more bibtex entries and notes

\textbf{Breakdown of resources}

@@

....lots more to add here.

@@

AAS workshop (\cite{aas-software-index}), CRediT project \cite{casrai-credit}, others...

>>>>

\textbf{Summary of submitted resources}

@@

Life sciences/NIH: Software Discovery Index Meeting Report \cite{software-discovery-index} a cross-disciplinary meeting
but with a largely NIH-focus. Suggested minimal information about software (MIAS) standard. Discusses how a common set of metadata
fields are critical for useful indexing - suggested candidates for this list.

Geosciences: Ontosoft \cite{ontosoft} - A Community Software Commons for the Geosciences. Lots of attention given to the metadata
required to describe, discover and execute research software. NSF geosciences workshop around data lifecycle, management and citation
\cite{nsf-geo-data}. This report includes many recommendations for data citation.

@@

AAS workshop (\cite{aas-software-index}), CRediT project \cite{casrai-credit}, Ontosoft \cite{ontosoft}
